---
title: "Forecasting # of visitors from Macao"
output: html_notebook
---


###CMV
```{r}
source("source.R")
TS_SE1 <- read.csv("macao.csv")
Visitors <- TS_SE1$Macao
Quarter <- TS_SE1$Month   
Season <- max(Quarter)
Period <- TS_SE1$period     
t  = Period -1               
n <- length(Visitors)

CMV_SI <- Center_Moving_Average(Visitors, Quarter, Season)
cat("# # # # The Centered moving average seasonal index # # # ","\n")
print(CMV_SI)

```


### Forecast by seasonal index
```{r}
Forecast_Visitors_CMV= Forecast_by_SI(Visitors, Quarter, Season, CMV_SI, t)

cat("# # # # The Forecast_Visitors_y # # # ","\n")
print(Forecast_Visitors_CMV)
#write.csv(Forecast_Visitors_CMV,"../../temp.csv")

t2 = c(t,n,n+1,n+2,n+3,n+4,n+5,n+6,n+7,n+8,n+9,n+10,n+11)
lines(t,Visitors, col = "blue", main = "Visitorsagainst Period", xlab = "Period", ylab = "Tourists")
lines(t, Visitors, type="o", col = "blue")    #actual
lines(t2,Forecast_Visitors_CMV, type="o", col = "red")  #forecast
legend("topleft", c("actual", "deseasonalized", "forecast"), fill=c("blue","green", "red"))
```
*Residual analysis: *            
  1.normality test       
  H0: Errors are normally distributed.        
  H1: Errors are not normally distributed.         
  Since pvalue = 0.2454 > 0.05, we do not reject H0.
  
  2..Homoscedasticity & Heteroscedasticity           
  H0: The variance of e is the same for all values of x.           
  H1: The variance of e is not the same for all values of x.         
  According to the plot, there is no sign of heteroscedasticity.        
    
  3.Dependence of the Error Variable         
  H0 : Randomness exists.        
  H1 : Randomness does not exist.      
  Since pvalue = 0.6989698 > 0.05, we do not reject H0.


*Assessment*                
  The standard error of estimate (1284) is large compared to mean_y (8772.741), indicating a weak linear relationship.
  
  r^2 = 86.83 of the variation in the fund value is explained by the variation in Des_x. The rest(13.17%) remains unexplained by this model.        
  
  Testing the coefficients beta1.      
  H0: beta1 = 0, H1: beta1 != 0          
  Since p-value <2e-16 , we are 95% confident to reject H0. There is overwhelming evidence that t affects Des_x.       
  
  
------------------------------------------------------------------------------------------
   
The # of visitors forecast for the next 12 months will be 7800.82, 15848.05, 11201.14, 12363.07, 11068.55, 18862.17, 17387.61, 26277.88, 16236.04, 10926.63, 10940.54, 22297.09 respectively.




## Smoothing by Linear Regression Model
```{r}
SLR_SI <- Linear_Regression_Seasonal_Index(Visitors, Quarter, Season)
cat("# # # # The Simple Linear_Regression seasonal index # # # ","\n")
print(SLR_SI)
```

### Forecast by seasonal index
```{r}
Forecast_Visitors_SLR <- Forecast_by_SI(Visitors, Quarter, Season, SLR_SI, t)

cat("# # # # The Forecast_Visitors_y # # # ","\n")
print(Forecast_Visitors_SLR)


lines(t, Visitors, type="o", col = "blue")    #actual
lines(t2,Forecast_Visitors_SLR, type="o", col = "red")  #forecast
legend("topleft", c("actual", "deseasonalized", "forecast"), fill=c("blue","green", "red"))
```
*Residual analysis: *            
  1.normality test       
  H0: Errors are normally distributed.        
  H1: Errors are not normally distributed.         
  Since pvalue = 0.2504 > 0.05, we do not reject H0.
  
  2..Homoscedasticity & Heteroscedasticity           
  H0: The variance of e is the same for all values of x.           
  H1: The variance of e is not the same for all values of x.         
  According to the plot, there is no sign of heteroscedasticity.        
    
  3.Dependence of the Error Variable         
  H0 : Randomness exists.        
  H1 : Randomness does not exist.      
  Since pvalue = 0.6989698 > 0.05, we do not reject H0.


*Assessment*                
  The standard error of estimate (1299) is large compared to mean_y (8774.535), indicating a weak linear relationship.
  
  r^2 = 86.59 of the variation in the fund value is explained by the variation in Des_x. The rest(13.41%) remains unexplained by this model.        
  
  Testing the coefficients beta1.      
  H0: beta1 = 0, H1: beta1 != 0          
  Since p-value <2e-16 , we are 95% confident to reject H0. There is overwhelming evidence that t affects Des_x.       
  
  
------------------------------------------------------------------------------------------
   
The # of visitors forecast for the next 12 months will be 7809.103, 15601.489, 11143.474, 12509.303, 10922.904, 19031.746, 17132.758, 26331.114, 16851.082, 10887.546, 11014.391, 22103.045 respectively.



## Regression model by indicator variables
### Line Chart by Quarters on excel
All the # of visitors for the twelve quarters have positive linear relationship with time.


### The Regression Model
y = beta0 + beta1\*t + beta2\*Q1 + beta3\*Q2 + beta4\*Q3 + beta5\*Q4 +beta6\*Q5 +beta7\*Q6 +beta8\*Q7 +beta\*9Q8 +beta10\*Q9 +beta11\*Q10 +vbeta12Q\*11 +e
where
t = time in chronological order
Qi = indicator variable (0, 1).

### Dummy as Quarter
```{r}
Dummy_I <- Season - 1    # n-1 indicator variables

Q <- matrix(nrow =n, ncol = Dummy_I)
Dummy_Name <- vector("character", length = Dummy_I)

for(i in 1:Dummy_I){
  Dummy_Name[i] <- paste0("Q", i)
}

colnames(Q) <- Dummy_Name

for(i in 1:n){
  for(j in 1:Dummy_I){
    if(Quarter[i] == j){
      Q[i,j] <- 1
    } else {
      Q[i,j] <- 0
    }  
  }
}
```

### build the model
```{r}
Data.Visitors <- cbind(t, Q)  #t, Q1, Q2, Q3...
linearModelVar1 <- lm(Visitors ~ Data.Visitors)
cat("\n# # # # The regression model # # # ","\n")
print(summary(linearModelVar1))
cat(" ","\n")
ANOVA_T_lm <- anova(linearModelVar1)
cat("# # # # The ANOVA Table # # # ","\n")
print(ANOVA_T_lm)


#residual analysis 
SE_1 <- standarized_errors_MR(Visitors, Data.Visitors)[,1]
h_1 <- standarized_errors_MR(Visitors, Data.Visitors)[,2]
D_1 <- standarized_errors_MR(Visitors, Data.Visitors)[,3]
print(shapiro.test(SE_1) )          # normality
b0<- coef(linearModelVar1)[1]             # Homoscedasticity & Heteroscedasticity 
b1 <- coef(linearModelVar1)[2]
b2 <- coef(linearModelVar1)[3]
b3 <- coef(linearModelVar1)[4]
b4 <- coef(linearModelVar1)[5]
b5 <- coef(linearModelVar1)[6]
b6 <- coef(linearModelVar1)[7]
b7 <- coef(linearModelVar1)[8]
b8 <- coef(linearModelVar1)[9]
b9 <- coef(linearModelVar1)[10]
b10 <- coef(linearModelVar1)[11]
b11 <- coef(linearModelVar1)[12]
b12 <- coef(linearModelVar1)[13]

yhat <- vector("double", length = n)
for(i in 1:n) {
       yhat <- b0 + b1 *t + b2 *Q[i,1] + b3 *Q[i,2] + b4 *Q[i,3]+ b5 *Q[i,4]+ b6 *Q[i,5]+ b7 *Q[i,6]+ b8 *Q[i,7]+ b9 *Q[i,8]+ b10 *Q[i,9]+ b11 *Q[i,10]+ b12 *Q[i,11]
}
plot(x = yhat, y = SE_1, xlab = "Predicted visitors", ylab = "Standardized Error", main = "predicted visitors vs Error")
cat("\nRun_Test:\n")
print(Run_Test(SE_1))              #errors are independent


cat("\nThe Outliers\n")
Outliers <- abs(SE_1) > 2
if(sum(Outliers)!=0){
    print(which(Outliers))
}else{
  print("no outliers")
}  
cat("\ninfluential observations:\n")

k <- dim(Data.Visitors)[2]
Inf_Obs <- h_1 > 3*(k+1)/n
if(sum(Inf_Obs)!=0){
    print(which(Inf_Obs))
}else{
  print("no influential observations")
} 


#assesment
cat("\nmean_y:",mean(Visitors),"\n")
```
*Residual analysis: *            
normality test       
  H0: Errors are normally distributed.        
  H1: Errors are not normally distributed.         
  Since pvalue = 0.04282 < 0.05, we reject H0. 
Therefore we do not use this method to forecast the # of visitors from Macao.
  
 
## Error Metrics
```{r}
CMV_MAD <- Mean_Absolute_Deviation(Visitors, Forecast_Visitors_CMV, 1)  #actual y, predicted y
CMV_MSE <- Mean_Square_Error(Visitors, Forecast_Visitors_CMV, 1)
CMV_MAPE <- Mean_Absolute_Percentage_Error(Visitors, Forecast_Visitors_CMV, 1)
SLR_MAD <- Mean_Absolute_Deviation(Visitors, Forecast_Visitors_SLR, 1)
SLR_MSE <- Mean_Square_Error(Visitors, Forecast_Visitors_SLR, 1)
SLR_MAPE <- Mean_Absolute_Percentage_Error(Visitors, Forecast_Visitors_SLR, 1)
Error_M <- matrix(nrow = 3, ncol = 2)
colnames(Error_M) = c("CMV", "SLR")
rownames(Error_M) = c("MAD", "MSE", "MAPE")
Error_M[1,1] <- CMV_MAD
Error_M[1,2] <- SLR_MAD
Error_M[2,1] <- CMV_MSE
Error_M[2,2] <- SLR_MSE
Error_M[3,1] <- CMV_MAPE
Error_M[3,2] <- SLR_MAPE
cat("\n# # # # Error Metrix # # # ","\n")
print(Error_M)
```
MAD: CMV is smaller by 8   
MSE: CMV is smaller by 59942 
MAPE: SLR is smaller by 0.03

Therefore, we choose CMV as the best method to forecast the # of visitors from Macao for the next 12 momnths. 
-------------------------------------------------------------------------------------------------   
##Conclusion:
By CMV, we forecast that the number of visitors from Macao for the next 12 months will be  7800.82, 15848.05, 11201.14, 12363.07, 11068.55, 18862.17, 17387.61, 26277.88, 16236.04, 10926.63, 10940.54, 22297.09 respectively.



